---
title: "Initial Testing of Markdown"
author: "Keith Baggerly"
date: "11/16/2018"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  github_document:
    default
---

```{r load_libraries}

library(reticulate)

```

```{python chunk1}

x = 5

```

```{r chunk2}

py$x

```


I want to talk about `code packages`.

```
more code stuff
possibly many lines
```

> a long quote here

We can also produce numbered lists

1. item 1
1. item 2
1. item 3



This is an example of using **R Markdown**.

The real strength, of course, is to be able
to include code as well. 

code bloksc involve backticks and options.

```{r name_of_my_code_chunk}

x <- 5
y <- 10
x + y

```

Furthermore, we can also do short things
inline, e.g. x is `r x`.

In addition to code, Markdown makes web 
communication reasonable. 

For example, the github site for this project is
https://github.com/kabagg/fda_2018_live

If I want to use a short name for the web
page, I can do that 
[too](https://github.com/kabagg/fda_2018_live)

We also want 

# Sections of Text

## Subsections of Text

### Subsubsections of Text

how about lists?

* item 1
* item 2
* item 33

